On the Functionality of the Multilayer Perceptron

### 2020-11-08 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Instrument Properties Section

@@

\textcolor{red}{I have notes written out for this section, I just need to write it out here soon}

@@

\paragraph*{}Rather than explore each class individually,

>>>>

\usepackage{multicol}

@@

@@

\paragraph*{}We have assembled training data samples than can be grouping in 38 classes of unique sources listed below:
\begin{multicols}{2}
\begin{enumerate}
	\item Alto Flute
	\item Alto Saxophone
	\item Banjo
	\item Bass
	\item Bass Clairnet
	\item Bass Flute
	\item Bassoon
	\item Bass Tromobe
	\item B$\flat$ Clarinet
	\item Bells

	\item Cello
	\item Clarinet \textcolor{blue}{Check this!}
	\item Contrabassoon
	\item Crotale
	\item E$\flat$ Clarinet
	\item English Horn
	\item Flute
	\item Guitar
	\item Hi-Hat
	\item Horn
		\columnbreak
	\item Mandolin
	\item Marimba
	\item Oboe
	\item Sawtooth Wave
	\item Saxophone (Tenor)
	\item Sine Wave
	\item Soprano Saxophone
	\item Square Wave
	\item Tenor Trombone
	\item Triangle Wave

	\item Trombone
	\item Trumpet (B$\flat$)
	\item Tuba
	\item Vibraphone
	\item Violin
	\item Viola
	\item White Nosie
	\item Xylophone
	\item
	\item
\end{enumerate}
\end{multicols}

\paragraph*{}Rather than explore each class individually, we can examine the properties of groupings of musical instrumentsby using the \textit{Hornbostel-Sachs} system \textit{red}{Citation needed!}. In this syetem, musical instruments or sound sources can be divided up into four broad categories based on the nature of the sound-producing material. These categories are (i) Idiophones, (ii) membranophones, (iii) Chordophones, and (iv) aerophones. In this section, we explore the mechanical properties of each group and show how the physics of the source instrument influences our feature choice.

\subsection*{Idiophones}
\label{subsec-Idiophone}

\paragraph*{}An idiophone is an instrument that produces sound through the vibration of the full body of the object. This generally includes most percussive instruments excluding drums \textcolor{red}{citation needed}. From the set of classes that we use, bells, crotales, Hi-hats, vibraphones, and xylophones are all examples of idiophones.
